The Response Time of Toronto's Paramedic Service: How effective is the city's emergency medical care?

### 2023-02-03 inputs/data/data_import.qmd
Add tests and simulation, improve code comments, remove extraneous files

```{r}
library(opendatatoronto)
library(tidyverse)
library(dplyr)

#raw_response_data <-
#  list_package_resources("8b068db1-95b8-4ea9-b942-8a7ce3a5fbd6") |>
#  filter(name == "Response Time (2013 - 2021)") |>
#  get_resource()

#write_csv(
#  x = raw_response_data$`Land Ambulance Services`,
#  file = "raw_response_data.csv"
#)

#raw_emergent_care_data <-
#  list_package_resources("174ace54-bcc7-4885-85c1-76094ab4a0ca") |>
#  filter(name == "Pre-hospital emergency care performance metrics 2014-2021") |>
#  get_resource() |>
#  filter(`Pre-Hospital Emergency Care Type` == "Emergency Request for Service")

#write_csv(
#  x = raw_emergent_care_data,
#  file = "raw_emergent_care_data.csv"
#)

#raw_response_numbered_data <-
#  list_package_resources("174ace54-bcc7-4885-85c1-76094ab4a0ca") |>
#  filter(name == "Pre-hospital emergency care performance metrics 2014-2021") |>
#  get_resource() |>
#  filter(`Pre-Hospital Emergency Care Type` == "Arrival to Life Threatening Calls 90% of Time")

#write_csv(
#  x = raw_response_numbered_data,
#  file = "raw_response_numbered_data.csv",
#)

raw_incident_data <-
  list_package_resources("c21f3bd1-e016-4469-abf5-c58bb8e8b5ce") |>
  filter(name == "paramedic-services-incident-data-2017-2021") |>
  get_resource()

write_csv(
  x = raw_incident_data$`2021`,
  file = "raw_incident_data.csv",
)
```

>>>>

```{r}
# Define required libraries
library(opendatatoronto)
library(tidyverse)
library(dplyr)

# Fetch Open Data Toronto's "Land Ambulance Response Time Standard" package: https://open.toronto.ca/dataset/land-ambulance-response-time-standard 
raw_response_data <-
  list_package_resources("8b068db1-95b8-4ea9-b942-8a7ce3a5fbd6") |>
  filter(name == "Response Time (2013 - 2021)") |>
  get_resource()

# Write data to a .csv file
write_csv(
  x = raw_response_data$`Land Ambulance Services`,
  file = "raw_response_data.csv"
)

# Fetch Open Data Toronto's "Pre-Hospital Emergency Care Performance Metrics" package:  https://open.toronto.ca/dataset/pre-hospital-emergency-care-performance-metrics
raw_emergent_care_data <-
  list_package_resources("174ace54-bcc7-4885-85c1-76094ab4a0ca") |>
  filter(name == "Pre-hospital emergency care performance metrics 2014-2021") |>
  get_resource() |>
  filter(`Pre-Hospital Emergency Care Type` == "Emergency Request for Service")

# Write data to a .csv file
write_csv(
  x = raw_emergent_care_data,
  file = "raw_emergent_care_data.csv"
)

# Fetch Open Data Toronto's "Paramedic Services Incident Data" package: https://open.toronto.ca/dataset/paramedic-services-incident-data
raw_incident_data <-
  list_package_resources("c21f3bd1-e016-4469-abf5-c58bb8e8b5ce") |>
  filter(name == "paramedic-services-incident-data-2017-2021") |>
  get_resource()

# Write data to a .csv file
write_csv(
  x = raw_incident_data$`2021`,
  file = "raw_incident_data.csv",
)
```

### 2023-02-03 outputs/paper/analysis.qmd
Add tests and simulation, improve code comments, remove extraneous files

```{r}
#| messages: false
#| echo: false
#| warning: false
library(lubridate)
library(tidyverse)
library(dplyr)
library(knitr)
library(janitor)
library(scales)
library(RColorBrewer)
library(ggplot2)
library(kableExtra)
raw_response_data <- readr::read_csv(here::here("inputs/data/raw_response_data.csv")) |>
  clean_names()
raw_emergent_care_data <- readr::read_csv(here::here("inputs/data/raw_emergent_care_data.csv"))
raw_incident_data <- readr::read_csv(here::here("inputs/data/raw_incident_data.csv")) |>
  clean_names()
```

@@

-   Paramedic Services Incident Data[^1]
-   Land Ambulance Response Time Standard[^2]
-   Pre-Hospital Emergency Care Performance Metrics[^3]\

This project contains information licensed under the Open Government Licence – Toronto^[Open Government License – Toronto: https://open.toronto.ca/open-data-license/].

[^1]: Paramedic Services Incident Data available at: https://open.toronto.ca/dataset/paramedic-services-incident-data

[^2]: Land Ambulance Response Time Standard available at: https://open.toronto.ca/dataset/land-ambulance-response-time-standard

[^3]: Pre-Hospital Emergency Care Performance Metrics available at: https://open.toronto.ca/dataset/pre-hospital-emergency-care-performance-metrics

@@

The primary tool used to analyse data in this paper is R, an open-source statistical programming language [@cite_tool_r]. The paper also uses a number of R packages, including: dplyr [@cite_tool_dplyr], ggplot2 [@cite_tool_ggplot2], here [@cite_tool_here], janitor [@cite_tool_janitor], kableExtra [@cite_tool_kableextra], knitr [@cite_tool_knitr], lubridate [@cite_tool_lubridate], opendatatoronto [@cite_tool_opendatatoronto], RColorBrewer [@cite_tool_rcolorbrewer], scales [@cite_tool_scales], and tidyverse [@cite_tool_tidyverse]. \newpage

## References

<!-- Span required to show references as a numbered section -->

>>>>

```{r}
#| messages: false
#| echo: false
#| warning: false
# Define required libraries 
library(lubridate)
library(tidyverse)
library(dplyr)
library(knitr)
library(janitor)
library(scales)
library(RColorBrewer)
library(ggplot2)
library(kableExtra)
library(here)
library(readr)

# Fetch the .csv file created from Open Data Toronto's "Land Ambulance Response Time Standard" package: https://open.toronto.ca/dataset/land-ambulance-response-time-standard
raw_response_data <- readr::read_csv(here::here("inputs/data/raw_response_data.csv"), show_col_types = FALSE) |>
  clean_names()

# Fetch Open Data Toronto's "Pre-Hospital Emergency Care Performance Metrics" package:  https://open.toronto.ca/dataset/pre-hospital-emergency-care-performance-metrics
raw_emergent_care_data <- readr::read_csv(here::here("inputs/data/raw_emergent_care_data.csv"), show_col_types = FALSE)

# Fetch Open Data Toronto's "Paramedic Services Incident Data" package: https://open.toronto.ca/dataset/paramedic-services-incident-data
raw_incident_data <- readr::read_csv(here::here("inputs/data/raw_incident_data.csv"), show_col_types = FALSE) |>
  clean_names()
```

@@

-   Paramedic Services Incident Data[^1]
-   Land Ambulance Response Time Standard[^2]
-   Pre-Hospital Emergency Care Performance Metrics[^3]

This project contains information licensed under the Open Government Licence -- Toronto[^4].\

[^1]: Paramedic Services Incident Data is available at: https://open.toronto.ca/dataset/paramedic-services-incident-data

[^2]: Land Ambulance Response Time Standard is available at: https://open.toronto.ca/dataset/land-ambulance-response-time-standard

[^3]: Pre-Hospital Emergency Care Performance Metrics is available at: https://open.toronto.ca/dataset/pre-hospital-emergency-care-performance-metrics

[^4]: Open Government License -- Toronto is available at: https://open.toronto.ca/open-data-license/

@@

The primary tool used to analyse data in this paper is R, an open-source statistical programming language [@cite_tool_r]. The paper also uses a number of R packages, including: dplyr [@cite_tool_dplyr], ggplot2 [@cite_tool_ggplot2], here [@cite_tool_here], janitor [@cite_tool_janitor], kableExtra [@cite_tool_kableextra], knitr [@cite_tool_knitr], lubridate [@cite_tool_lubridate], opendatatoronto [@cite_tool_opendatatoronto], readr [@cite_tool_readr], RColorBrewer [@cite_tool_rcolorbrewer], scales [@cite_tool_scales], and tidyverse [@cite_tool_tidyverse]. \newpage

## References
<!-- Span required to show references as a numbered section -->
